Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex
tabs and caret return

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected :
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]

>>>>

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]
		which means that there could be systems with no first periodic DIT.
